### 2017-03-01 readme.Rmd
changes to file structure

<!-- Generate some random points and a raster to represent study area. -->
<!-- ```{r} -->
<!-- library(raster) -->
<!-- set.seed(123) -->
<!-- N <- 100 -->
<!-- ks <- as.data.frame(cbind(x1=runif(N, min=-10, max=10),x2=runif(N, min=-10, max=10))) -->
<!-- sa <- raster(nrows=100, ncols=100, xmn=-10, xmx=10,ymn=-10,ymx=10) -->
<!-- sa[]<-rnorm(10000) -->
<!-- projection(sa) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" -->
<!-- plot(sa) -->
<!-- points(ks$x1,ks$x2,pch=16) -->
<!-- ``` -->

<!-- How many quasi-random background points do we need? Let start with 200. -->
<!-- The function will plot the underlying probability of sampling intensity, the presence points (white) and the generated quasi-random background points. -->
<!-- ```{r} -->
<!-- library(qrbp) -->
<!-- set.seed(123) -->
<!-- n <- 200 -->
<!-- bkpts <- qrbp(n,dimension = 2,known.sites=ks,include.known.sites=TRUE, -->
<!--               study.area = sa,inclusion.probs = NULL,sigma=1,plot.prbs=TRUE) -->
<!-- points(ks$x1,ks$x2,pch=16,col='white') -->
<!-- ``` -->

@@

`eip` is a function which can be used to estimate inclusion probabilities. This layer of probabilities can be used as a bias offset in PPM modelling.

@@

```{r}
bias_layer <- eip(known_sites = species@coords,
                  study_area = preds[[1]],
                  sigma = 10000)

>>>>

@@

`estimate_bias_layer` is a function which can be used to inform the selection of quasirandom bias points to be used in as a bias offset in PPM modelling.

@@

```{r}
bias_layer <- estimate_bias_layer(known_sites = species@coords,
                                  study_area = preds[[1]],
                                  sigma = 10000)
